The imprint of global magma oceans on exoplanet demographics

### 2023-03-24 src/tex/ms.tex
minor edits about instellation

\section{Runaway Greenhouse Model}\label{sec:met_rghmodel}
\todo[inline]{TIM: please review}
%\todo[inline]{
%\textbf{Main assumptions:}\\
%- every planet (modulo $f_\mathrm{rgh}$) has \textit{some} water. Enough for runaway GH under the right conditions.  \\
%- Limitation to small planets without significant atmospheric envelopes.\\
%- we ignore water loss by H$_2$O photolysis in the upper atmosphere and subsequent H escape, which would eventually cool even planets within the runaway greenhouse regime~\citep{Lichtenberg2022}.\\
%- we ignore tidal heating, which could extend the magma ocean phase of close-in planets (and change their orbits via tidal orbital evolution)( Jackson et al., 2008; Barnes et al., 2013 (?)).\\
%}
The climate state of a planet has a direct influence on its size as measured by transit photometry~\citep{Turbet2019}.
We use predictions on transit atmospheric thickness from geophysical models to derive the change in transit radius and bulk density that planets with instellation-induced runaway greenhouse climates experience.
...

\todo[inline]{ARNAUD: revise definition of $S$ following our discussion on 2022-12-22. Introduce net instellation and clarify what is meant by it.}
\begin{note}
    The power from the host star per unit area at the position of a planet or net instellation $S$ in units of Earth's insolation is given by
    \begin{equation}
        \frac{S}{S_\oplus} = \left(\frac{L_\star}{L_\odot}\right) \left(\frac{au}{a}\right)^2 .
    \end{equation}
    We assume global redistribution of incoming flux and a fixed albedo of $0.3$, comparable to Earth's~\citep{Haar1971}.
    The absolute value of $S_\oplus$, by which all synthetic planets are scaled, is then \SI{238}{\watt\per\square\meter}.
%    We further define the solar-equivalent semi-major axis $a_{eff} = a (L_\star/L_\odot)^{-1/2}$, at which a planet experiences the same instellation as a Solar System planet at an orbital distance~$a$.
   We do not take into account additional heating sources such as tidal effects~\citep[e.g.][]{Barnes2013}.
\end{note}

>>>>

\section{Runaway Greenhouse Model}\label{sec:met_rghmodel}
\todo[inline]{TIM: please review}
%\todo[inline]{
%\textbf{Main assumptions:}\\
%- every planet (modulo $f_\mathrm{rgh}$) has \textit{some} water. Enough for runaway GH under the right conditions.  \\
%- Limitation to small planets without significant atmospheric envelopes.\\
%- we ignore water loss by H$_2$O photolysis in the upper atmosphere and subsequent H escape, which would eventually cool even planets within the runaway greenhouse regime~\citep{Lichtenberg2022}.\\
%- we ignore tidal heating, which could extend the magma ocean phase of close-in planets (and change their orbits via tidal orbital evolution)( Jackson et al., 2008; Barnes et al., 2013 (?)).\\
%}
The climate state of a planet has a direct influence on its apparent size measured by transit photometry~\citep{Turbet2019}.
We use predictions on transit atmospheric thickness from geophysical models to derive the change in transit radius and bulk density that planets with instellation-induced runaway greenhouse climates experience.
...

\todo[inline]{ARNAUD: revise definition of $S$ following our discussion on 2022-12-22. Introduce net instellation and clarify what is meant by it.}
\begin{note}
    The power absorbed by the planet from the host star per unit area at its orbital distance or net instellation $S$ in units of Earth's insolation is given by
    \begin{equation}
        \frac{S}{S_\oplus} = \left(\frac{L_\star}{L_\odot}\right) \left(\frac{au}{a}\right)^2 .
    \end{equation}
    We assume global redistribution of incoming flux and a wavelength and spherically integrated albedo, or Bond albedo, of $0.3$, comparable to Earth's~\citep{Haar1971}.
    The absolute value of $S_\oplus$, by which all synthetic planets are scaled, is then \SI{238}{\watt\per\square\meter}.
%    We further define the solar-equivalent semi-major axis $a_{eff} = a (L_\star/L_\odot)^{-1/2}$, at which a planet experiences the same instellation as a Solar System planet at an orbital distance~$a$.
   We do not take into account additional heating sources such as tidal effects~\citep[e.g.][]{Barnes2013}.
\end{note}
